ghgvcr
======

R implementation of the Greenhouse Gas Value Calculator

Citation: Kristina J. Teixeira and Evan H. Delucia 2011. The greenhouse gas value of ecosystems. Global Change Biology. 17(1):425–438 doi: 10.1111/j.1365-2486.2010.02220.x

-------

### Inputs

* `inst/config.xml` example input file
* `inst/extdata/ghgvc1.Rdata` all objects used and provided by ghgvc 1.0
* `inputs.Rdata` example of inputs as R objects for ghgvcr example (below)
* `inst/extdata/multipft_input.xml`

### Outputs 

produced by example below:

* `inst/extdata/output.csv`
* `inst/extdata/output.json`

### Installing the ghgvcr package on the PEcAn 1.2.6 VM

The bash and R code snippets below install dependencies, and only need to be run once. 

```{r eval=FALSE}
sudo apt-get install git
sudo apt-get install libcurl4-openssl-dev # dependency of Rcurl, 

git clone https://github.com/dlebauer/pecan.git pecan
git clone https://github.com/dlebauer/ghgvcR.git ghgvcR
R 
```

```{r eval = FALSE, include=TRUE}
install.packages(c("devtools", "roxygen2"), 
                 repos= "http://cran.us.r-project.org")
library(devtools)
install(ghgvcr)
install(pecan/utils)
```

### Example of how to run the calculator

* This can be run at the command line: `./src/ghgvc_script.R`

```{r echo = FALSE, message=FALSE}
library(ghgvcr)
```

```{r results='hide', comment=NA, warning=FALSE}

options(warn=FALSE)
#test("../ghgvcR")
#example(ghgvcr)


## the following is equivalent to 
config.xml <- system.file("config.xml", package = "ghgvcr")
config.list <- xmlToList(xmlParse(config.xml))
ecosystem_data <- config.list$ecosystem_data

x <- ghgvcr::ghgvc(options = config.list$options,
                   ecosystem_data = config.list$ecosystem_data)


writeLines(x, "inst/extdata/output.json")
write.csv(as.data.frame(fromJSON(x)), "inst/extdata/output.csv")

```

```{r results='hide', comment=NA, warning=FALSE}
multipft_config.xml <- system.file("multipft_config.xml", package = "ghgvcr")
multipft_config.list <- xmlToList(xmlParse(multipft_config.xml))

x2 <- ghgvcr::ghgvc2(multipft_config.list)

writeLines(x2, "inst/extdata/multipft_output.json")
write.csv(as.data.frame(fromJSON(x2)), "inst/extdata/multipft_output.csv")

```

### Plots:

```{r results='hide', comment=NA, warning=FALSE}
library(ggplot2)
# number of ecosystems:
n.ecosystems <- length(names(ecosystem_data)) 
for(i in 1:n.ecosystems){
  result  <- ecosystem_data[[i]]
  ecosystem.name <- result$name
  if(i == 1){
    result.df <- as.data.frame(result)
    
    } else {
      result.df <- rbind(result.df, as.data.frame(result))      
    }
  rownames(result.df)[i] <- gsub(" ", "", ecosystem.name)
}

# identify cols with numbers
result.num <- suppressWarnings(as.numeric(result))
num.logical <- !(is.na(result.num) | result.num == -9999)
result.df <- result.df[,!(result.num == -9999 | is.na(result.num))]

# transpose data.frame for plotting:
result.tdf <- cbind(variable = names(result.df),
                    as.data.frame(t(result.df)))

forcings.index <- grepl("F", names(result.df))
forcings.names <- names(result.df)[forcings.index]


forcings <- result.tdf[forcings.index,]
forcings.long <- melt(forcings, id.vars= "variable")
colnames(forcings.long) <- c("variable", "ecosystem", "value")


```


```{r  fig.width=10, fig.height=4}
ggplot(data = forcings.long, 
       aes(x = variable, y = value, fill = ecosystem)) + 
  geom_bar(position="dodge", stat = "identity") + ggtitle(label="Example plot: values of F for two ecosystems") + 
  xlab("Variable") + ylab("Units of F") + coord_flip()

```
