ghgvcr
======

R implementation of the Greenhouse Gas Value Calculator

Citation: Kristina J. Teixeira and Evan H. Delucia 2011. The greenhouse gas value of ecosystems. Global Change Biology. 17(1):425–438 doi: 10.1111/j.1365-2486.2010.02220.x

[![Travis-CI Build Status](https://travis-ci.org/ebimodeling/ghgvcR.svg?branch=master)](https://travis-ci.org/ebimodeling/ghgvcR)

-------

### Inputs

* `inst/config/config.xml` example input file
* `inst/extdata/ghgvc1.Rdata` all objects used and provided by ghgvc 1.0
* `inputs.Rdata` example of inputs as R objects for ghgvcr example (below)
* `inst/extdata/multipft_input.xml`

### Outputs 

produced by example below:

* `inst/extdata/output.csv`
* `inst/extdata/output.json`

### Installing the ghgvcr package on the PEcAn 1.2.6 VM

The bash and R code snippets below install dependencies, and only need to be run once. 

```sh
sudo apt-get install git
sudo apt-get install libcurl4-openssl-dev # dependency of Rcurl, 

git clone https://github.com/dlebauer/pecan.git pecan
git clone https://github.com/dlebauer/ghgvcR.git ghgvcR
R 
```

```{r include = TRUE, message = FALSE}
library(ghgvcr)
library(XML)
library(jsonlite)
options(warn=FALSE)

```

### Example of how to run the calculator

* This can be run at the command line: `./src/ghgvc_script.R`

```{r results='hide', comment=NA, warning=FALSE}

config_file <- system.file("config/config.xml", package = "ghgvcr")

config <- xmlToList(xmlParse(config_file, validate=F))  

#Calculator
ghgvc_output <- ghgvc(config, , make_plots = FALSE, write_data = FALSE)

ghgvc_output.json <- toJSON(ghgvc_output)


```

```{r results='hide', comment=NA, warning=FALSE}
multisite_config.xml <- system.file("config/multisite_config.xml", package = "ghgvcr")
multipft_config.list <- xmlToList(xmlParse(multisite_config.xml))

x2 <- ghgvc(multipft_config.list, make_plots = FALSE, write_data = FALSE)

writeLines(x2, "inst/extdata/multipft_output.json")
write.csv(as.data.frame(fromJSON(x2)), "inst/extdata/multipft_output.csv")

```
