ghgvcR
======

R implementation of the Greenhouse Gas Value Calculator

Citation: Kristina J. Teixeira and Evan H. Delucia 2011. The greenhouse gas value of ecosystems. Global Change Biology. 17(1):425–438 doi: 10.1111/j.1365-2486.2010.02220.x

-------

### Inputs

* `inst/config.xml` example input file
* `inst/extdata/ghgvc1.Rdata` all objects used and provided by ghgvc 1.0
* `inputs.Rdata` example of inputs as R objects for ghgvcR example (below)

### Outputs 

produced by example below:

* `inst/extdata/output.csv`
* `inst/extdata/output.json`

### Installing the ghgvcR package on the PEcAn 1.2.6 VM

```{bash eval = false}
sudo apt-get install git
sudo apt-get install libcurl4-openssl-dev # dependency of Rcurl, 

git clone https://github.com/dlebauer/ghgvcR.git ghgvcR
R 
```

```{r }
install.packages(c("devtools", "roxygen2"), 
                 repos= "http://cran.us.r-project.org")
library(devtools)

load_all("ghgvcR")
```


now check it out:
```{r}
# test("ghgvcR")
# example(ghgvcR)
setwd("ghgvcR")
## the following is equivalent to 
config.xml <- system.file("config.xml", package = "ghgvcR")


config.list <- xmlToList(xmlParse(config.xml))
options <- config.list$options

ecosystem_data <- config.list$ecosystem_data

x <- ghgvcR::ghgvc(options, ecosystem_data)

writeLines(x, "inst/extdata/output.json")
write.csv(as.data.frame(fromJSON(x)), "inst/extdata/output.csv")

```
