---
title: "Getting Started with GHGVCR"
author: "Nicholas Potter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with GHGVCR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The Greenhouse Gas Value Calculator ([GHGVC](http://www.ecosystemservicescalc.org/)) uses the `ghgvcR` package to calculate greenhouse gas emissions. GHGVC can be installed at [https://github.com/ebimodeling/ghgvc](https://github.com/ebimodeling/ghgvc).

Citation: Kristina J. Teixeira and Evan H. Delucia 2011. The greenhouse gas value of ecosystems. Global Change Biology. 17(1):425438 doi: 10.1111/j.1365-2486.2010.02220.x

####Overview
`ghgvcR` has two principal functions:

1. `get_ncdf()` reads in netcdf biome data.
2. `ghgvcr()` calculates the greenhouse gas emissions of a specific ecosystem. 

These functions are implemented in two scripts in the `inst/scripts` directory of the `ghgvcR` package: `get_biome.R` and `calc_ghgv.R`. `get_biome.R` is used by GHGVC to load biome data from netcdf4 files. `calc_ghgv.R` is used by GHGVC to calculate greenhouse gas emissions and write the results to a json file.

####Quick Example
Several example ecosystem data files are kept in `inst/config_examples/`. These can be used in place of biome data to run the calculator entirely within R:

```{r}
library(ghgvcr)

#load example config data
config_file <- system.file("config/multisite_config.xml", package = "ghgvcr")
config <- XML::xmlToList(XML::xmlParse(config_file))  

#Calculate 
res <- ghgvc(config, write_data=FALSE, make_plots=FALSE)

#Write the data to a file:
#outdir <- "./"
#write_json(res, outdir, filename = "ghgvc_example", format="json")
```

`ghgvcR` can also plot the greenhouse gas values that are returned by `ghgvc()`:

``` {r, fig.show='hold'}
df <- as.data.frame(res$site_1_data)
#p <- ghgvc_plot(df, save = FALSE)
#p

```

####Biome Example 
The same calculation can be done for a specific location if biome data is available.

```{r eval=FALSE}
#NOT RUN 
library(ghgvcr)
data(biome_defaults)

#Example location
latitude <- 40.18
longitude <- -89.82

#paths
netcdf_dir <- "<data directory>"

#Load the biome data for that location
biome <- get_biome(latitude, longitude, netcdf_dir, biome_defaults, write_data = FALSE)
head(biome)

#Calculate GHGV
#res <- ghgvc(biome)
```

####Working with GHGVC
`ghgvcR` works in concert with `ghgvc` through the `ghgvcR` scripts. This requires a certain amount of configuration. Once `ghgvc` is set up correctly, the following settings must be configured in `app/workflows_controller.rb`:

**Where to find the `ghgvcR` scripts**
`ghgvcR_scripts_path` needs to be set. In development this is currently "<ghgvcR repository directory>/inst/scripts". In production, it may be better to place the scripts directory within the `ghgvc` app itself (e.g. "<ghgvc directory>/ghgvcR/").

**Where the netcdf data is stored**
By default the netcdf data is stored at "<ghgvc directory>/netcdf/".

**Where the name-indexed ecosystem json file is stored**
By default this is "<ghgvc directory>/public/data/final_ecosystems.json".

